### 2022-11-14 NSF2022/Description/specificaim1v2.tex
...

In the case of granules, bending enters through the
splay of the granule directors. In
Figure~\ref{fig:JPv_linearshear}, for example, the directors have
negative, respectively positive, splay $\nabla_{\Sigma} \cdot \dd$ in
the outer, respectively inner monolayers. Here $\nabla_{\Sigma}\cdot{} =
\nabla \cdot {} - \mathbf{N}\mathbf{N}^T \nabla$ is the surface
divergence for the outward unit surface normal $\NN$. From differential
geometry, we have that $\nabla\cdot \dd = \pm 2H$ whenever $\dd$ is
everywhere parallel to $\NN$, and this is how curvature enters
the granule-based description.  For two-dimensional vesicles,
$H$ is replaced with the curvature $\kappa$ of the curve $\mathcal{C}$.
Granules are at rest when attraction balances repulsion, and will have
stretching energy when the distance between neighboring granules is increased
from rest.

>>>>

In the case of granules, bending enters through the
splay of the granule directors. In
Figure~\ref{fig:JPv_linearshear}, for example, the directors have
negative, respectively positive, splay $\nabla_{\Sigma} \cdot \dd$ in
the outer, respectively inner monolayers. Here $\nabla_{\Sigma}\cdot{}$
the surface divergence. From differential
geometry, we have that $\nabla\cdot \dd = \pm 2H$ whenever $\dd$ is
everywhere normal to $\Sigma$, and this is how curvature enters
the granule-based description.  For two-dimensional vesicles,
$H$ is replaced with the curvature $\kappa$ of the curve $\mathcal{C}$.
Granules are at rest when attraction balances repulsion, and will have
stretching energy when the distance between neighboring granules is increased
from rest.
